Model LF

### 2022-10-14 max_dp endogen stød.Rmd
Commit ændringer

@@

plot(prod_03, col= "red"); lines(prod_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((ur_ds_03 - ur_ds_bs3) / ur_ds_bs3), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

@@

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "red");
legend("left", legend=c("Scenario 4","Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","red"));
grid()

plot(((ur_ds_05 - ur_ds_00) / ur_ds_00), col= "blue", xlab= "Year", ylab= "% Change in UR", main= "UR");
lines(((ur_ds_04 - ur_ds_00) / ur_ds_00), col= "black");
lines(((ur_ds_02 - ur_ds_00) / ur_ds_00), col= "red");
legend("left", legend=c("Scenario 4","Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red"));
grid()
```

@@

@@

```{r}
plot((emp_s3_low-emp_sbs3_low)*1000, col= "red")
```

>>>>

## Baseline Scenario 7

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs7 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7 = Shock_bs7$simulation$max_dp
wage_bs7 = Shock_bs7$simulation$wage
komp_r_bs7 = Shock_bs7$simulation$komp_r
part_bs7 = Shock_bs7$simulation$part
yk_ds_bs7 = Shock_bs7$simulation$yk_ds
pc_ds_bs7 = Shock_bs7$simulation$pc_ds
wage_ds_t_bs7 = Shock_bs7$simulation$wage_ds_t
ur_ds_bs7 = Shock_bs7$simulation$ur_ds
emp_bs7 = Shock_bs7$simulation$emp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds

tilpas_pr_bs7 = Shock_bs7$simulation$tilpas_pr
u_ds_bs7 = Shock_bs7$simulation$u_ds
part_bs7 = Shock_bs7$simulation$part
nben_h_bs7 = Shock_bs7$simulation$nben_h
wage_ds_bs7 = Shock_bs7$simulation$wage_ds
dp_person_bs7 = Shock_bs7$simulation$dp_person
kont_h_ratio_bs7 = Shock_bs7$simulation$kont_h_ratio

nl_g_bs7 = Shock_bs7$simulation$nl_g

yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prod_bs7 = Shock_bs7$simulation$prod
```

@@

plot(prod_03, col= "red", main= "Productivity"); lines(prod_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((emp_03 - emp_bs3) / emp_bs3), col= "black", xlab= "Year", ylab= "% Change in Employment", main= "Employment")
```

@@

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","red", "black","orange", "green"));
grid()

plot(((emp_05 - emp_bs56)/ emp_bs56), col= "blue", xlab= "Year", ylab= "% Change in UR", main= "UR");
lines(((emp_04 - emp_bs4)/ emp_bs4), col= "black");
legend("left", legend=c("All channels","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red"));
grid()
```

@@

# Scenario 7 All but prod

```{r}
# Define add-factor list (defining shock)
constantAdjList7 <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_7 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList7
                    )

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "% Change in employment", main= "Employment", ylim= c(-350, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

```{r}
plot((emp_s3_low-emp_sbs3_low)*1000, col= "red", ylab= "Change in employment (people)", main= "Employed estimate set to 0.1"); grid()
```
